The Array of Long-Baseline Antennas for Taking Radio Observations from the Sub-Antarctic

### 2020-07-20 albatros_paper.tex
HCC added more observations text

\begin{figure}
  \begin{center}
    \includegraphics[width=0.9\linewidth]{Figures/albatros2_waterfalls.jpg}
    \caption{Spectra from a co-aligned polarization pair from the
      two-element \albatros\ pathfinder, shown as a function of
      frequency and time.  The auto- and cross-spectra are shown in
      the top and bottom rows, respectively.  The spectrum magnitudes
      are in uncalibrated ADC units on a logarithmic scale, and the
      cross-spectrum is about two orders of magnitude fainter than the
      autospectra.  Repeatable structure from the Galaxy is visible
      over the three-day time scale in all plots.}
    \label{Fig:albatros2_waterfalls}
  \end{center}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=0.6\linewidth]{Figures/albatros2_lst_phase.jpg}
    \caption{Phases from the cross-correlation between two co-aligned
      polarizations in the two-element \albatros\ pathfinder.  About
      372 hours of data are shown here, binned in local sidereal
      time.}
    \label{Fig:albatros2_phase}
  \end{center}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=0.8\linewidth]{Figures/baseband_direct_auto_compare.jpg}
    \caption{Placeholder figure for comparison of auto-spectra from
      baseband (4-bit), and directly computed/averaged by the SNAP.}
    \label{Fig:baseband_direct_auto}
  \end{center}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[width=0.8\linewidth]{Figures/baseband_direct_phase_compare.jpg}
    \caption{Placeholder figure for comparison of cross-spectrum phase from
      baseband (4-bit), and directly computed/averaged by the SNAP.}
    \label{Fig:baseband_direct_phase}
  \end{center}
\end{figure}

\attention{Do we want a plot showing solar power data of any sort?}

>>>>

\begin{figure}[t]
  \begin{center}
    \includegraphics[width=0.9\linewidth]{Figures/albatros2_waterfalls.jpg}
    \caption{Spectra from a co-aligned polarization pair from the
      two-element \albatros\ pathfinder, shown as a function of
      frequency and time.  The auto- and cross-spectra are shown in
      the top and bottom rows, respectively.  The spectrum magnitudes
      are in uncalibrated ADC units on a logarithmic scale, and the
      cross-spectrum is about two orders of magnitude fainter than the
      autospectra.  Repeatable structure from the Galaxy is visible
      over the three-day time scale in all plots.}
    \label{Fig:albatros2_waterfalls}
  \end{center}
\end{figure}

\begin{figure}[t]
  \begin{center}
    \includegraphics[width=0.6\linewidth]{Figures/albatros2_lst_phase.jpg}
    \caption{Phases from the cross-correlation between two co-aligned
      polarizations in the two-element \albatros\ pathfinder.  About
      372 hours of data are shown here, binned in local sidereal
      time.}
    \label{Fig:albatros2_phase}
  \end{center}
\end{figure}

@@

\begin{figure}[t]
  \begin{center}
    \includegraphics[width=0.8\linewidth]{Figures/baseband_direct_auto_compare.jpg}
    \caption{Placeholder figure for comparison of auto-spectra from
      baseband (4-bit), and directly computed/averaged by the SNAP.}
    \label{Fig:baseband_direct_auto}
  \end{center}
\end{figure}

\begin{figure}[t]
  \begin{center}
    \includegraphics[width=0.8\linewidth]{Figures/baseband_direct_phase_compare.jpg}
    \caption{Placeholder figure for comparison of cross-spectrum phase from
      baseband (4-bit), and directly computed/averaged by the SNAP.}
    \label{Fig:baseband_direct_phase}
  \end{center}
\end{figure}

@@

% note to self: look up time of day that corresponds to LST period
% where fringes appear to extend below 10 MHz, see if that's night
% time

We have been unable to retrieve data from the single autonomous
station pathfinder on Marion because of COVID-19 and limited bandwidth
to the island, although we have confirmed that the solar power system
has successfully met the power demands of the antenna station.  To
demonstrate baseband writing capability in the absence of Marion data,
we instead present a short observation that was taken by a separate
\albatros\ pathfinder station that operated from the McGill Arctic
Research Station (MARS; \ang{79;26;}N, \ang{90;46;}W) during
July~2019.  The RF signal chain of the MARS installation had the same
architecture as that shown in \autoref{Fig:albatros1_schem}, but the
power was supplied by manually charged batteries, rather than a solar
power system.  The MARS RFI environment is somewhat noisier than that
of Marion Island, and because the data were taken during the height of
Arctic summer, the ionospheric plasma cutoff frequency is higher than
the typical cutoff reflected in the Marion data.

\autoref{Fig:baseband_direct_auto} shows autospectra for one
polarization of the \albatros\ pathfinder installed at MARS, comparing
the accumulated spectra that are directly computed by the SNAP board
against spectra that are calculated from baseband data with 4-bit
quantization.  (Autospectrum information is not preserved with 1-bit
quantization.)  Baseband data were recorded over two frequency
windows, 5.3--12.6~MHz and 12.6--20.0~MHz, at separate times, and the
corresponding accumulated spectra from the SNAP board are shown for
the same frequency and time ranges.  The waterfall plots have the same
61-kHz frequency resolution, set by the resolution of the spectra
computed by the SNAP board.  The overplotted mean spectra are shown
with finer resolution (\attention{numbers go here}) from the baseband
data to illustrate the additional information that is not retained in
the accumulated spectra.  For these mean spectrum plots, the baseband
data are processed by
inverting\footnote{\url{https://github.com/jrs65/pfb-inverse}} the
polyphase filter bank to recover time-domain data, and the forward
polyphase filter bank is then applied to concatenated timestreams of
an appropriate total length to set the desired frequency resolution.
The spectra computed from baseband qualitatively agree with those
directly accumulated by the SNAP board, up to small differences caused
by the 4-bit quantization.

\attention{more words to come here about phase plots}
